Example Paper

### 2023-10-05 latex-article/article.tex
Switch to .sty finally
Improve article template:
- Improve font choice (option for sans-serif and serif)
- IBM Plex mono for `\texttt` font
- New `\note` command from @pmichaillat.
  - This replaces `threeparttable`
- Math symbols to seperate file following @pmichaillat

\documentclass[12pt]{article}

% Include Theme
\input{preamble.tex}

% \maketitle info
\title{Example Paper}
\author{
    Author One%
    \thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.} \ and Author Two%
    \thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.}
}
\date{\today}

% Conditionally include comments. Switch to \togglefalse
\newtoggle{INCLUDECOMMENTS}
\toggletrue{INCLUDECOMMENTS}
% \togglefalse{INCLUDECOMMENTS}
\newcommand{\kyle}[1]{\iftoggle{INCLUDECOMMENTS}{{\color{cranberry}\textbf{Kyle:} #1}}{}}

@@

% Paper ------------------------------------------------------------------------

% ------------------------------------------------------------------------------
\section{Introduction}
% ------------------------------------------------------------------------------

@@

% ------------------------------------------------------------------------------
\subsection{Subsection}
% ------------------------------------------------------------------------------

@@

Has iriure invenire no, vidit tamquam ad nec, sea unum efficiantur no. In fugit eruditi quaerendum qui. Eleifend interpretaris mel id. Cu tation veniam habemus ius. Prima tritani duo ei, est iuvaret dignissim an, efficiendi adversarium per ut. Sit eu lucilius postulant, ut nam falli vitae theophrastus. Vel ex audire referrentur.

Tibique reformidans ut eum, oratio singulis efficiantur eam eu. Modus simul quo cu, id populo essent urbanitas nec. Cum agam aeterno cu, soleat iuvaret posidonium mel cu. Eirmod noluisse ad vix.

\[
  \condexpec{Y_i(1) - Y_i(0)}{\one(D_i = 1)} = \prob{\tau}
\]

@@

  \begin{threeparttable}
    \begin{adjustbox}{width = \textwidth, center}
      \begin{tabular}{@{} @{\extracolsep{5pt}}
          l*{8}{r}
          @{}}
        % Head
        \toprule
        & & & \multicolumn{2}{c}{Market Access} & \multicolumn{2}{c}{Urban Weekly Wage} & \multicolumn{2}{c}{Nonurban Weekly Wage} \\
        \cmidrule{4-5} \cmidrule{6-7} \cmidrule{8-9}
        Year & \multicolumn{1}{c}{N} & \% Urban & Mean & SD & Mean & SD & Mean & SD \\
        \hline

@@

    % Notes 
    \begin{tablenotes}
      \item \textit{Notes.} Weekly wage is reported in 2015 \$.
    \end{tablenotes}
  \end{threeparttable}
\end{table}

@@

% ------------------------------------------------------------------------------
\newpage
\appendix
\numberwithin{equation}{section}
\numberwithin{figure}{section}
\numberwithin{table}{section}
\renewcommand{\thefigure}{\Alph{section}\arabic{figure}}
\renewcommand{\thetable}{\Alph{section}\arabic{table}}
% ------------------------------------------------------------------------------

>>>>

\documentclass[12pt]{article}
\usepackage{paper}
\usepackage{math}

\title{Example Paper}
\author{
  Author One%
  \thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.} \ and Author Two%
  \thanks{School. Email: \href{mailto:email@gmail.com}{email@gmail.com}.}
}
\date{\today}

% Conditionally include comments. Switch to \togglefalse
\newtoggle{INCLUDECOMMENTS}
\toggletrue{INCLUDECOMMENTS}
% \togglefalse{INCLUDECOMMENTS}
\newcommand{\kyle}[1]{\iftoggle{INCLUDECOMMENTS}{
  \cranberry{\textbf{Kyle:} #1}
}{}}

\hfuzz=100pt

@@

% Paper ------------------------------------------------------------------------
% ------------------------------------------------------------------------------
\section{Introduction}
% ------------------------------------------------------------------------------

@@

% ------------------------------------------------------------------------------
\subsection{Math Commands}
% ------------------------------------------------------------------------------

Credit to \url{https://pascalmichaillat.org/d3/} for his math commands package

The command \texttt{\textbackslash E[optional]\{optional\}\{optional\}} now lets you specify subscript, the inner term, and a second bracket to do conditional expectation. All three are optional and \textbackslash expec is a alias.
$$\E \quad \E[i] \quad \E{X_i} \quad \E[i]{X_i} \quad \E{X_i}{n} \quad \E[i]{X_i}{n}$$

\texttt{\textbackslash P}, \texttt{\textbackslash prob}, \texttt{\textbackslash cov}, and \texttt{\textbackslash var} work the same way too:
$$\P \quad \P[i] \quad \P{X_i} \quad \P[i]{D_i} \quad \P{\bar{X}_n > \bar{X}}{\mu = \mu_0} \quad \P[\mathcal{F}]{X_i}{D_i = 1}$$
$$\cov{X_n, Y_n} \quad \var[i](\bar{X}_n)$$

\texttt{\textbackslash one} does an indicator. Same as above, but no conditional:
$$\one{X_i > 0}$$

We have \texttt{\textbackslash aslim}, \texttt{\textbackslash plim}, and \texttt{\textbackslash convd} for convergence symbols. There's also \texttt{\textbackslash iid}. Examples:
$$\bar{x}_n \aslim \mu \quad \bar{x}_n \plim \mu \quad \bar{x}_n \convd N(0, 1)$$
$$X_i \iid N(0, 1)$$

To wrap things in automatically scaling wrappers, can use \texttt{\textbackslash bp} for parenthesis, \texttt{\textbackslash bc} for curly braces, and \texttt{\textbackslash bs} for square brackets:
$$\bp{y_i} \quad \bc{y_i} \quad \bs{y_i}$$

Similar to expectations, I have `upgraded' \texttt{\textbackslash min}, \texttt{\textbackslash inf}, \texttt{\textbackslash liminf}, \texttt{\textbackslash max}, \texttt{\textbackslash sup}, and \texttt{\textbackslash limsup} commands to use the optional `\texttt{[]}' for subscript:
$$\min[i]{x_i} \quad \inf[i]{x_i} \quad \liminf[n \to \infty]{x_i}$$
$$\max[i]{x_i} \quad \sup[i]{x_i} \quad \limsup[n \to \infty]{x_i}$$

Theorem environments look nice. There are the following environments and their numbering resets automatically for appendices: \texttt{theorem}, \texttt{proposition}, \texttt{assumption}, \texttt{example}, \texttt{lemma}, \texttt{corollary}, \texttt{definition}, \texttt{remark}

@@

@@

  \begin{adjustbox}{width = \textwidth, center}
    \begin{tabular}{ 
      @{} @{\extracolsep{5pt}} l*{8}{r} @{}
    }
      % Head
      \toprule
      & & & \multicolumn{2}{c}{Market Access} & \multicolumn{2}{c}{Urban Weekly Wage} & \multicolumn{2}{c}{Nonurban Weekly Wage} \\
      \cmidrule{4-5} \cmidrule{6-7} \cmidrule{8-9}
      Year & \multicolumn{1}{c}{N} & \% Urban & Mean & SD & Mean & SD & Mean & SD \\
      \hline

@@

  \note{Weekly wage is reported in 2015 \$.}
\end{table}

@@

% ------------------------------------------------------------------------------
\newpage
\appendix
% ------------------------------------------------------------------------------
